### 2015-11-30 fundamentals/intro.tex
On line 17, replaced 'inflexible architectures' with 'inflexible architectures, never having been designed to enable new features or extensions.'
line 67, changed to radiotoxicity and mined uranium requirements. left out the suggestion of noting the energy normalization, given that the derived metrics are discussed later in the paragraph

To date, current tools are typically distributed under restrictive rather than open
source licenses, having been developed in industrial contexts or using 
commercial software platforms. Additionally, having
often been developed for customized applications, many possess inflexible
architectures. Finally, many model only fleet-level dynamics of facilities and
materials rather than discrete resolution of those individual agents and
objects. When the DOE-NE Fuel Cycles Technologies Systems Analysis Campaign
developed requirements necessary in a next generation fuel cycle simulator,
three main failure modes were associated with those software choices.
First, they discourage targeted
contribution and collaboration among experts. Next, they hobble efforts to
directly compare modeling methodologies. Finally, they over-specialize,
rendering most tools applicable to only a subset of desired simulation
fidelities, scales, and applications. Those three constraints were identified
as presenting significant challenges to modeling fidelity, generality, efficiency,
robustness, and scientific transparency in the field of fuel cycle analysis
\cite{huff_next_2010}.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, a
combination of fuel and operating costs normalized by electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions, these metrics are derived from
mass balances and facility operation histories calculated by a fuel cycle
simulator. For example, where nuclear waste repository burden is derived from
ejected fuel masses, water pollution or land use can be derived from facility
operational histories (as in \cite{poinssot_assessment_2014}).

>>>>

To date, current tools are typically distributed under restrictive rather than open
source licenses, having been developed in industrial contexts or using 
commercial software platforms. Additionally, having
often been developed for customized applications, many possess inflexible
architectures, never having been designed to enable new features or extensions.
Finally, many model only fleet-level dynamics of facilities and
materials rather than discrete resolution of those individual agents and
objects. When the DOE-NE Fuel Cycles Technologies Systems Analysis Campaign
developed requirements necessary in a next generation fuel cycle simulator,
three main failure modes were associated with those software choices.
First, they discourage targeted
contribution and collaboration among experts. Next, they hobble efforts to
directly compare modeling methodologies. Finally, they over-specialize,
rendering most tools applicable to only a subset of desired simulation
fidelities, scales, and applications. Those three constraints were identified
as presenting significant challenges to modeling fidelity, generality, efficiency,
robustness, and scientific transparency in the field of fuel cycle analysis
\cite{huff_next_2010}.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, a
combination of fuel and operating costs normalized by electricity generation, while
environmental performance might be measured by spent fuel volume, radiotoxicity, or
mined uranium requirements. A meta-analysis of fuel cycle systems studies 
identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions, these metrics are derived from
mass balances and facility operation histories calculated by a fuel cycle
simulator. For example, where nuclear waste repository burden is derived from
ejected fuel masses, water pollution or land use can be derived from facility
operational histories (as in \cite{poinssot_assessment_2014}).
